---
title: "Introduction to Social Networks with `netmem`"
subtitle: "A 2-hour hands-on workshop"
author: "Alejandro Espinosa-Rada — Institute of Sociology, Pontificia Universidad Católica de Chile"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 2
    number_sections: true
    code_folding: show
    df_print: paged
    fig_width: 6
    fig_height: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  collapse = TRUE,
  fig.align = "center"
)
set.seed(2026)
```

> **What this workshop is.** Two hours to go from *"a network is just dots and
> lines"* to *measuring* networks yourself, in R. We use
> [`netmem`](https://anespinosa.github.io/netmem/), a package that treats every
> network as a **matrix** and builds its measures on top of matrix algebra. If
> you can read a spreadsheet, you can read a network.
>
> **Who it is for.** People who are new to social networks but comfortable
> running basic R (assigning objects, calling functions, indexing a matrix).
>
> **How to use it.** Run every chunk yourself. Each section ends with a short
> *Your turn* exercise; click **Solution** to check your answer.

---

# Setup {#setup}

`netmem` is on CRAN, so installation is a one-liner. We also load `igraph` and
`sna` — the two canonical network packages — for two reasons: to **draw**
networks, and to show that the measures we compute with `netmem` match what the
standard tools give. (`ggraph` is used for one polished plot near the end.)

```{r install, eval=FALSE}
install.packages("netmem")   # the star of the show: measures from matrices
install.packages("igraph")   # canonical analysis + plotting
install.packages("sna")      # canonical analysis (works straight from matrices)
install.packages("ggraph")   # one nice ggplot-style network plot
```

```{r libs}
library(netmem)
library(igraph)
packageVersion("netmem")
```

> **Two warnings about the canonical packages.**
>
> 1. `igraph` and `sna` define many functions with the *same name* (`degree`,
>    `closeness`, ...) that expect different inputs. To stay out of trouble we
>    call them explicitly as `igraph::degree()` and `sna::degree()` rather than
>    attaching `sna` with `library()`.
> 2. They speak different "native languages": `igraph` wants a **graph object**
>    (build it once with `graph_from_adjacency_matrix()`), while `sna` — like
>    `netmem` — reads an **adjacency matrix directly**.

A tiny helper so our pictures look consistent throughout:

```{r plot-helper}
plot_net <- function(M, mode = "directed", main = "", vcol = "#4C72B0") {
  g <- igraph::graph_from_adjacency_matrix(M, mode = mode, diag = FALSE)
  plot(g,
    main = main,
    vertex.color = vcol, vertex.frame.color = "white",
    vertex.size = 18, vertex.label.color = "black", vertex.label.cex = 0.8,
    edge.arrow.size = 0.4, edge.color = "grey60",
    layout = igraph::layout_with_fr
  )
}
```

---

# Module 1 — A network *is* a matrix {#mod1}

A social network has two ingredients: **nodes** (people, organisations, papers)
and **ties** between them (friendship, advice, citation). The most useful way to
store that on a computer is the **adjacency matrix** `A`: one row and one column
per node, and `A[i, j] = 1` when *i* sends a tie to *j*.

```{r first-matrix}
A <- matrix(c(
  0, 1, 1, 0,
  0, 0, 1, 0,
  0, 0, 0, 1,
  1, 0, 0, 0
), byrow = TRUE, nrow = 4)
rownames(A) <- colnames(A) <- c("Ana", "Beto", "Cata", "Dani")
A
```

Read it as a sentence: *Ana points to Beto and Cata; Cata points to Dani; Dani
points back to Ana.* Let's see the same thing as a drawing:

```{r first-plot, fig.height=4}
plot_net(A, main = "Four people, five arrows")
```

`netmem` gives you a quick health-check of any matrix before you trust it —
is it square? symmetric? binary? are there missing values or self-loops?

```{r matrix-report}
matrix_report(A)
```

## Two ways to feed a network into R

Most real data does **not** arrive as a matrix. It arrives as an **edge list**
(a two-column table: *who* → *whom*). `netmem` converts freely between the two,
which is half the daily work of network analysis.

```{r edgelist}
# matrix  ->  edge list
E <- matrix_to_edgelist(A, digraph = TRUE)
E

# edge list  ->  matrix (back where we started)
edgelist_to_matrix(E, digraph = TRUE)
```

## One-mode vs. two-mode

So far nodes were all the same kind (people->people): a **one-mode** network.
Often the raw data instead links *two different kinds* of node — people to the
events, committees, or papers they belong to. That is a **two-mode** (or
*bipartite*) network, stored as an **incidence matrix**: rows are people,
columns are groups.

```{r incidence}
# 6 people (rows) by 4 committees (columns)
I <- matrix(c(
  1, 0, 0, 1,
  1, 1, 0, 0,
  0, 1, 1, 0,
  0, 1, 1, 0,
  0, 0, 1, 1,
  1, 0, 0, 1
), byrow = TRUE, nrow = 6)
rownames(I) <- paste0("person", 1:6)
colnames(I) <- paste0("comm", 1:4)
I
```

We come back to two-mode networks in Module 6 — for now just notice that the
*shape* of the matrix already tells you what kind of network you have.

> **Your turn 1.** Build the adjacency matrix of a 3-person *undirected*
> friendship triangle (everyone friends with everyone) and confirm with
> `matrix_report()` that it is symmetric.

<details><summary>**Solution**</summary>
```{r sol1}
T3 <- matrix(c(
  0, 1, 1,
  1, 0, 1,
  1, 1, 0
), byrow = TRUE, nrow = 3)
matrix_report(T3)
```
</details>

---

# Module 2 — Your first real network {#mod2}

Time for real data. `netmem` ships with **Krackhardt's high-tech managers**: 21
managers in a firm, each reporting who they consider a **friend**. It is a
classic teaching dataset.

```{r krack-load}
data(krackhardt_friends)
K <- krackhardt_friends
dim(K)                 # 21 managers x 21 managers
K[1:6, 1:6]            # a corner of the matrix
```

Friendship here is **directed**: *I* may name *you* as a friend without you
naming me. Let's look at it:

```{r krack-plot}
rownames(K) <- colnames(K) <- paste0("M", 1:21)
plot_net(K, main = "Krackhardt managers: who calls whom a friend")
```

## How dense, how reciprocated?

Two of the first questions in any study: *how many of the possible ties
actually exist?* (**density**) and *when I name you, do you name me back?*
(**reciprocity**).

```{r krack-dens}
gen_density(K, directed = TRUE)              # share of possible ties present
recip_coef(K, method = "global")             # share of ties that are returned
```

About a quarter of possible friendships exist, and roughly 45% of nominations
are reciprocated — friendship is partly, but far from fully, mutual.

## Who is central?

The simplest notion of importance is **degree**: how many ties a node has.
Because the network is directed we separate **in-degree** (how many people name
*you* — a measure of popularity) from **out-degree** (how many people *you*
name). `gen_degree()` is `netmem`'s generalised degree, working for directed,
weighted, and two-mode networks alike.

```{r krack-degree}
indeg  <- gen_degree(K, type = "in")
outdeg <- gen_degree(K, type = "out")

# the four most-named (most popular) managers
sort(indeg, decreasing = TRUE)[1:4]
```

```{r krack-degree-norm}
# normalised in-degree: fraction of others who name you (Freeman, 1978)
round(sort(gen_degree(K, type = "in", normalized = TRUE), decreasing = TRUE)[1:5], 3)
```

## The same numbers, the canonical way

Whatever `netmem` reports, you should be able to reproduce with `igraph` or
`sna`. This is worth doing once so you trust the tools — and so you can read code
written in either ecosystem.

```{r krack-canonical}
# igraph needs a GRAPH object, built once from the matrix:
g <- igraph::graph_from_adjacency_matrix(K, mode = "directed", diag = FALSE)

# --- density ---
gen_density(K, directed = TRUE)   # netmem
igraph::edge_density(g)           # igraph
sna::gden(K)                      # sna: straight from the matrix (deals better with missing values!)

# --- reciprocity ---
recip_coef(K, method = "global")  # netmem
igraph::reciprocity(g)            # igraph

recip_coef(K, method = "total_ratio")  # netmem
sna::grecip(K)                         # sna

# --- in-degree (top 3 most popular) ---
sort(gen_degree(K, type = "in"), decreasing = TRUE)[1:3]          # netmem
sort(igraph::degree(g, mode = "in"), decreasing = TRUE)[1:3]      # igraph
sort(sna::degree(K, cmode = "indegree"), decreasing = TRUE)[1:3]  # sna
```

Three packages, identical answers. From here on we show the canonical
equivalent for each new measure in a compact comment block.

> **Your turn 2.** Is anyone a "hub" who names many others but is named by few
> (high out-degree, low in-degree)? Compute `outdeg - indeg` and find the
> manager with the largest gap.

<details><summary>**Solution**</summary>
```{r sol2}
gap <- outdeg - indeg
sort(gap, decreasing = TRUE)[1:3]   # names many, named by few
```
</details>

---

# Interlude — Drawing networks {#viz}

A good picture is the fastest way to *understand* a network before you measure
it. Two things drive a readable plot: the **layout** (where nodes go) and the
**aesthetics** (mapping size and colour to something meaningful). We let `netmem`
do the measuring and `igraph`/`ggraph` do the drawing.

## Layouts: same network, different stories

There is no single "correct" layout — each algorithm emphasises something
different. Try a few and keep the one that communicates.

```{r layouts, fig.width=9, fig.height=3.4}
op <- par(mfrow = c(1, 3), mar = c(0, 0, 2, 0))
plot(g, layout = igraph::layout_with_fr(g),     main = "Force-directed (FR)",
     vertex.size = 12, vertex.label = NA, edge.arrow.size = 0.2, vertex.color = "#4C72B0")
plot(g, layout = igraph::layout_with_mds(g),   main = "Multidimensional Scaling",
     vertex.size = 12, vertex.label = NA, edge.arrow.size = 0.2, vertex.color = "#DD8452")
plot(g, layout = igraph::layout_with_kk(g),     main = "Kamada-Kawai",
     vertex.size = 12, vertex.label = NA, edge.arrow.size = 0.2, vertex.color = "#55A868")
par(op)
```

## Aesthetics: let the measures drive the picture

The point of a network plot is to *show structure*. Here we size each node by
its **in-degree** (popularity, from `gen_degree()`) and colour it by its
**k-core** (how deep in the cohesive centre it sits, from `k_core()`). Now the
picture and the numbers tell the same story.

```{r aesthetics, fig.width=7, fig.height=6}
KS    <- K * t(K)                            # mutual ties (used again in Module 3)
indeg <- gen_degree(K, type = "in")          # netmem: node importance
core  <- k_core(KS)                          # netmem: cohesion depth
pal   <- c("#C44E52", "#DD8452", "#55A868")  # colour per core level

plot(g,
  layout       = igraph::layout_with_fr(g),
  vertex.size  = 6 + 2.2 * sqrt(indeg),      # area ~ popularity
  vertex.color = pal[core + 1],
  vertex.frame.color = "white",
  vertex.label.cex = 0.7, vertex.label.color = "black",
  edge.arrow.size = 0.25, edge.color = "grey75",
  main = "Krackhardt friends — size = in-degree, colour = k-core"
)
legend("bottomleft", legend = paste("k-core", 0:2), pt.bg = pal,
       pch = 21, pt.cex = 1.6, bty = "n", title = "Cohesion")
```

Isolates (small, dark-red, core 0) sit on the rim; the dense core of popular,
mutually-tied managers glows green in the middle.

## A polished version with `ggraph`

`ggraph` brings the grammar of graphics to networks: edges and nodes become
`geom_`s you can map aesthetics onto, exactly like `ggplot2`.

```{r ggraph, fig.width=7, fig.height=6}
library(ggraph)
library(ggplot2)

igraph::V(g)$indeg <- indeg
igraph::V(g)$core  <- factor(core)

ggraph(g, layout = "fr") +
  geom_edge_fan(arrow = arrow(length = unit(1.6, "mm"), type = "closed"),
                end_cap = circle(2.5, "mm"),
                edge_colour = "grey75", edge_alpha = 0.6) +
  geom_node_point(aes(size = indeg, colour = core)) +
  geom_node_text(aes(label = 1:vcount(g)), size = 2.4, repel = TRUE) +
  scale_size(range = c(2, 9)) +
  scale_colour_manual(values = pal) +
  labs(size = "In-degree", colour = "k-core",
       title = "Krackhardt managers, the ggraph way") +
  theme_graph(base_family = "sans")
```

> **Tip.** For *publication* figures the workflow above (compute with `netmem`,
> draw with `ggraph`).

---

# Module 3 — Local structure: dyads, triangles, cores {#mod3}

Centrality is about single nodes. The sociological heart of network analysis is
about **configurations** — the small patterns that repeat across the network and
reveal how it is glued together.

## The dyad census

Look at every **pair** of nodes. A pair is **mutual** (both name each other),
**asymmetric** (one-way), or **null** (no tie). Counting all three is the *dyad
census* — the simplest summary of a directed network's texture.

```{r dyad-census}
dyadic_census(K)
```

```{r dyad-canonical}
# canonical equivalents (same three counts):
igraph::dyad_census(g)   # g is the igraph object from Module 2
sna::dyad.census(K)
```

## Transitivity: are my friends friends with each other?

*"A friend of my friend is my friend."* When that closure happens a lot, the
network is **transitive** and full of triangles — the signature of tight social
worlds. We work with the **mutual** (undirected) friendships here.

```{r transitivity}
KS <- K * t(K)                       # keep only reciprocated ties -> undirected
trans_coef(KS, method = "global")    # global clustering coefficient

gKS <- igraph::graph_from_adjacency_matrix(KS, mode = "undirected", diag = FALSE)
igraph::transitivity(gKS, type = "global")   # canonical equivalent

sna::gtrans(K)                           # weak census as clustering coefficient
trans_coef(K, method = c("weakcensus"))  # weak census as clustering coefficient
```

## Cores and components

- **Components** are the disconnected islands of the network.
- The **k-core** peels the network like an onion: the *k*-core is the part where
  everyone still has at least *k* connections. High cores are dense, cohesive
  centres.

`components_id()` returns a list: a `$components` membership vector and a
`$size` table. The number of islands is the number of entries in `$size`.

```{r cores}
comp <- components_id(KS)
length(comp$size)                    # how many islands (4 isolates + 1 big core)
table(k_core(KS))                    # how many nodes sit in each core level
```

```{r cores-canonical}
igraph::components(gKS)$no            # number of components, canonical
table(igraph::coreness(gKS))         # coreness == k-core membership
```

## Cliques

A **clique** is a fully connected group — everyone tied to everyone. The
smallest interesting one is the triangle (3-clique).

```{r cliques}
rownames(KS) <- 1:NROW(KS); colnames(KS) <- rownames(KS)
cl <- clique_table(KS, number = TRUE)
cl$table                             # the cliques themselves
cl$n_triangles                       # number of triangles in the mutual network
```

> **Your turn 3.** The dyad census reported the mutual/asymmetric/null counts.
> Compute by hand the proportion of **non-null** dyads that are mutual, and
> check it is close to the global reciprocity from Module 2.

<details><summary>**Solution**</summary>
```{r sol3}
dc <- dyadic_census(K)
unname(dc["Mutual"] / (dc["Mutual"] + dc["Asymmetrics"]))
```
</details>

---

# Module 4 — Ego networks & structural holes {#mod4}

Zoom in on one person — **ego** — and the people they are tied to — their
**alters**. The shape of that little neighbourhood predicts real outcomes:
Ronald Burt showed that people whose contacts *don't know each other* sit on
**structural holes** and tend to get the promotions and the good ideas.

We use a small, hand-built network so the geometry is visible. Node `g` is
connected to everyone; the others are only loosely connected among themselves.

```{r ego-net}
A <- matrix(c(
  0, 1, 0, 0, 1, 1, 1,
  1, 0, 0, 1, 0, 0, 1,
  0, 0, 0, 0, 0, 0, 1,
  0, 1, 0, 0, 0, 0, 1,
  1, 0, 0, 0, 0, 0, 1,
  1, 0, 0, 0, 0, 0, 1,
  1, 1, 1, 1, 1, 1, 0
), ncol = 7, byrow = TRUE)
rownames(A) <- colnames(A) <- letters[1:7]
plot_net(A, mode = "undirected", main = "g brokers between everyone else", vcol = "#DD8452")
```

Extract `g`'s personal network — just ego's neighbours and the ties among them:

```{r ego-extract}
ego_net(A, ego = "g")
```

## Redundancy and effective size

If your contacts all know each other, they give you **redundant** information.
Burt's **effective size** discounts that redundancy; **efficiency** scales it by
how many contacts you have.

```{r redundancy}
redundancy(A, ego = "g")
```

## Constraint

**Constraint** is high when you are stuck inside a tight, closed group with few
independent options — the opposite of brokerage. `eb_constraint()` implements
the Everett–Borgatti formulation of Burt's measure.

```{r constraint}
eb_constraint(A, ego = "g")   # the broker, tied to everyone
eb_constraint(A, ego = "b")   # an ordinary node tied to a, d, g
```

> **Your turn 4.** Whose position is more constrained — `a` or `g`? Compute the
> constraint for both and explain the result in one sentence.

<details><summary>**Solution**</summary>
```{r sol4}
eb_constraint(A, ego = "a")$results
eb_constraint(A, ego = "g")$results
# g brokers between otherwise-disconnected alters, so g is far less constrained.
```
</details>

---

# Module 5 — Homophily: do birds of a feather flock? {#mod5}

People tend to befriend others *like themselves* — same gender, office, or
profession. That tendency is **homophily**, and it is one of the most robust
findings in social science. `netmem` measures it directly from the matrix plus a
node attribute.

We switch to **Lazega's law firm**: 71 lawyers, with their friendship network
and rich attributes (office, seniority, practice area...).

```{r lazega-load}
data(lazega_lawfirm)
fr  <- lazega_lawfirm$friends           # 71 x 71 friendship matrix
att <- lazega_lawfirm$attributes        # attribute matrix (one column per variable)
colnames(att)
```

Give the matrix labels and keep mutual friendships:

```{r lazega-prep}
rownames(fr) <- colnames(fr) <- paste0("L", 1:nrow(fr))
frS    <- fr * t(fr)                     # reciprocated friendships
office <- att[, "office"]                # 1 = Boston, 2 = Hartford, 3 = Providence
```

## The mixing matrix

The **mixing matrix** cross-tabulates ties by the groups of the two people
involved. Big numbers on the **diagonal** mean people befriend within their own
group — the fingerprint of homophily.

```{r mixing}
mix_matrix(frS, att = office)
```

Almost all friendships sit on the diagonal: lawyers overwhelmingly befriend
colleagues in **their own office**.

## One number: the E–I index

Krackhardt & Stern's **E–I index** boils homophily down to a single number
between −1 and +1:

- **−1** = every tie is *internal* (perfect homophily),
- **+1** = every tie is *external* (perfect heterophily),
- **0** = ties ignore the attribute.

```{r ei}
ei_index(frS, mixed = FALSE, att = office)                 # by office
ei_index(frS, mixed = FALSE, att = att[, "practice"])      # by practice area
```

Office produces strong homophily (a large negative value); practice area far
less so.

The canonical counterpart in `igraph` is the **assortativity coefficient**.
Watch the **sign convention**: assortativity runs the *opposite* way to the E–I
index — homophily is **positive** for assortativity but **negative** for E–I.

```{r assortativity}
gfr <- igraph::graph_from_adjacency_matrix(frS, mode = "undirected", diag = FALSE)
igraph::assortativity_nominal(gfr, as.integer(factor(office)))   # +0.69: strong homophily
```

Both agree the firm is strongly segregated by office — they just label it with
opposite signs.

## How diverse is the firm to begin with?

Homophily is only meaningful against the available diversity. **Blau's index**
(and its normalised cousin, the IQV) measures how spread out a categorical
attribute is — 0 means everyone is identical, higher means more varied.

```{r blau}
heterogeneity(office, normalized = TRUE)
```

> **Your turn 5.** Compute the E–I index for **gender** (`att[, "gender"]`). Are
> friendships more segregated by gender or by office?

<details><summary>**Solution**</summary>
```{r sol5}
ei_index(frS, mixed = FALSE, att = att[, "gender"])
# Compare to the office value above: office segregates friendship far more strongly.
```
</details>

---

# Module 6 — Beyond the simple graph {#mod6}

This is where `netmem`'s matrix philosophy pays off. The same algebra extends to
networks that classic tools handle awkwardly: **two-mode**, **signed**, and
**multilevel**.

## Two-mode networks and their projections

Recall the people-by-committees incidence matrix from Module 1. We can
**project** it into two one-mode networks: people linked by *shared committees*,
and committees linked by *shared members*.

```{r projection}
proj <- matrix_projection(I)
proj$matrix1     # committees connected by shared members (overlap counts)
```

```{r bip-degree}
gen_density(I, bipartite = TRUE)                 # density of a two-mode network
gen_degree(I, bipartite = TRUE, type = "all")    # how many committees each person sits on
```

## Signed networks: friends *and* enemies

Real relationships are not only present/absent — they can be **positive (+1)** or
**negative (−1)**. **Structural balance** theory (Heider) says the stable
configurations are *"the enemy of my enemy is my friend."* `struc_balance()`
checks how balanced a signed network is.

```{r signed}
S <- matrix(c(
   0,  1, -1,
   1,  0, -1,
  -1, -1,  0
), byrow = TRUE, nrow = 3)
rownames(S) <- colnames(S) <- c("a", "b", "c")
struc_balance(S)                                 # a & b are friends, both dislike c
```

A `balance_score` of 1 means this triangle is perfectly balanced: two friends
united against a common adversary.

## Multilevel networks

Sometimes nodes live at **different levels** — say individuals *and* the
organisations they belong to — with ties within and between levels. `netmem`
stacks the pieces into one **meta-matrix** and computes degree across the whole
structure.

```{r multilevel}
A1 <- matrix(c(                # level 1: ties among 5 individuals
  0, 1, 0, 0, 1,
  1, 0, 0, 1, 1,
  0, 0, 0, 1, 1,
  0, 1, 1, 0, 1,
  1, 1, 1, 1, 0
), byrow = TRUE, nrow = 5)

B1 <- matrix(c(                # affiliation: which of 3 groups each individual joins
  1, 0, 0,
  1, 1, 0,
  0, 1, 0,
  0, 1, 0,
  0, 1, 1
), byrow = TRUE, nrow = 5)

A2 <- matrix(c(                # level 2: ties among the 3 groups
  0, 1, 1,
  1, 0, 0,
  1, 0, 0
), byrow = TRUE, nrow = 3)

# the full multilevel system as a single matrix
meta_matrix(A1, B1, A2 = A2)
```

```{r multilevel-degree}
# degree that counts ties to BOTH peers and groups
multilevel_degree(A1, B1, A2 = A2)
```

> **Your turn 6.** In the two-mode `I` data, use `matrix_projection(I)$matrix2`
> to get the *people* projection. Which two people share the most committees?

<details><summary>**Solution**</summary>
```{r sol6}
people <- matrix_projection(I)$matrix2
diag(people) <- 0
which(people == max(people), arr.ind = TRUE)   # the most-overlapping pair(s)
```
</details>

---

# Wrap-up {#wrap}

In two hours you went from *"a network is dots and lines"* to:

- storing a network as a **matrix** and converting to/from edge lists
  (`matrix_report`, `matrix_to_edgelist`, `edgelist_to_matrix`);
- describing it — **density, degree, reciprocity, transitivity, cores, cliques**
  (`gen_density`, `gen_degree`, `recip_coef`, `trans_coef`, `k_core`,
  `clique_table`, `dyadic_census`);
- zooming into **ego networks and structural holes**
  (`ego_net`, `redundancy`, `eb_constraint`);
- measuring **homophily** (`mix_matrix`, `ei_index`, `heterogeneity`);
- and stepping **beyond the simple graph** to two-mode, signed, and multilevel
  networks (`matrix_projection`, `struc_balance`, `meta_matrix`,
  `multilevel_degree`).

Along the way you saw every measure **reproduced in `igraph` and `sna`** — so
you can trust the numbers and read code from any ecosystem — and learned to
**draw** networks (layouts + aesthetics in `igraph` and `ggraph`) so the picture
and the measures tell one story.

The thread running through all of it: **once your network is a matrix, every
measure is just algebra you can read, check, and trust.**

## A take-home challenge

The Lazega data also contains an **advice** network
(`lazega_lawfirm$advice`) and a **cowork** network (`lazega_lawfirm$cowork`).
Pick one and reproduce Modules 2–5 on it: Who is most sought for advice
(in-degree)? Is advice-seeking reciprocated? Do lawyers ask advice within their
own office (homophily)? Compare your answers to the friendship network.

## Where to go next

- **Package site & full function reference:** <https://anespinosa.github.io/netmem/>
- **Source & issues:** <https://github.com/anespinosa/netmem>
- **More classic datasets:** the [`classicnets`](https://github.com/anespinosa/classicnets) package
- **Foundational reading:** Wasserman & Faust (1994), *Social Network Analysis:
  Methods and Applications*; Burt (1992), *Structural Holes*.

```{r citation}
citation("netmem")
```

---

```{r session, echo=FALSE}
sessionInfo()
```
